Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-11 analysis/paper_draft3.Rmd
add sentences on fisher's test and CMH

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and based on historical strike data for that attorney. Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020].

>>>>

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and based on historical strike data for that attorney. Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020]. Methods such as the Fishers exact test and the Cochran-Mantel-Haenszel (CMH) test (Gastwirth and Xu, 2014) can be used to test for bias and could include data from past trials, either by pooling all strike sequence data (in the case fo Fisher's test), or by stritifying the data by trial (CHM test). While these approaches may increase statistical power, they do not directly address possible incompatibility between current and historical trial data and may, therefore, only be appropriate when, as suggested by Gastwirth and Hu (2014), historical trail data are selected that are 'similar' to the current trial. This notion of simliarity require implicit weighint of historical evidence.
